Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Move some text from Realising to Conclusions.

TCP Hollywood inherits standard TCP's congestion control mechanism.
Clearly, being a loss-based algorithm, this is not appropriate for
real-time applications.
\todo{discuss how we need to change TCP congestion control}

@@

Making effective use of the TAPS concept to support real-time multimedia
requires making significant changes to the TCP specification and API, if 
such applications are to be able to fall-back to TCP from UDP, and still
achieve their performance needs.

>>>>

% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}

@@

% Making effective use of the TAPS concept to support real-time multimedia
% requires making significant changes to the TCP specification and API, if 
% such applications are to be able to fall-back to TCP from UDP, and still
% achieve their performance needs.
